---
output:
  html_document: default
  word_document: default
  pdf_document: default
---
```{r}
# Load necessary packages.
library(tidyverse)
library(ggplot2)
library(reshape2)
library(vtable)
library(dplyr)
library(knitr)
#install.packages("hms")

tidyverse_conflicts(only = NULL)

knitr::opts_chunk$set(echo = FALSE)
options(knitr.table.format = "latex")

```

```{r}
#install.packages("kableExtra", dependencies = TRUE)
```


Step 1: Read in the StoreData.csv file into a table.

```{r}
# Import Data from CSV with header
beliefs <- read.csv(file.choose(),header=TRUE) ## Choose MAMbeliefs.csv file
```

```{r}
head(beliefs)
```

Step 2: Get some basic info about the variables.

```{r}
# Summarize the data.
st(beliefs)
```

```{r}
# Grab comparison columns.
data <- select(beliefs, c(subj, contains("Price")))
data <- select(data, -contains("Imp"))

# Make a tidy data set
melt_data <- melt(data, id="subj")

# Compare means across brands for each attribute.
ggplot(melt_data, aes(x=variable, y=value, fill=variable)) +
  geom_boxplot() + guides(fill=FALSE)
```
Brand D seems to have the most market share on the Price feature. Brand C has a similar mean so they might equally share the market.

```{r}
# Remove existing data frame
rm(data)

# Grab comparison columns.
data <- select(beliefs, c(subj, contains("Style")))
data <- select(data, -contains("Imp"))

# Remove existing data frame
rm(melt_data)

# Make a tidy data set
melt_data <- melt(data, id="subj")

# Remove existing data frame
rm(data)

# Compare means across brands for each attribute.
ggplot(melt_data, aes(x=variable, y=value, fill=variable)) +
  geom_boxplot() + guides(fill=FALSE)
```
Brand B seems to have the highest overall market share on the Style feature to consumers.

```{r}
# Remove existing data frame
rm(data)

# Grab comparison columns.
data <- select(beliefs, c(subj, contains("Durability")))
data <- select(data, -contains("Imp"))

# Remove existing data frame
rm(melt_data)

# Make a tidy data set
melt_data <- melt(data, id="subj")

# Remove existing data frame
rm(data)

# Compare means across brands for each attribute.
ggplot(melt_data, aes(x=variable, y=value, fill=variable)) +
  geom_boxplot() + guides(fill=FALSE)

```
Brand C has the most market share in the Durability feature to consumer taking the survey.

```{r}
# Remove existing data frame
rm(data)

# Grab comparison columns.
data <- select(beliefs, c(subj, contains("Comfort")))
data <- select(data, -contains("Imp"))

# Remove existing data frame
rm(melt_data)

# Make a tidy data set
melt_data <- melt(data, id="subj")

# Remove existing data frame
rm(data)

# Compare means across brands for each attribute.
ggplot(melt_data, aes(x=variable, y=value, fill=variable)) +
  geom_boxplot() + guides(fill=FALSE)

```

```{r}

# Remove existing data frame
rm(data)

# Grab comparison columns.
data <- select(beliefs, c(subj, contains("Features")))
data <- select(data, -contains("Imp"))

# Remove existing data frame
rm(melt_data)

# Make a tidy data set
melt_data <- melt(data, id="subj")

# Remove existing data frame
rm(data)

# Compare means across brands for each attribute.
ggplot(melt_data, aes(x=variable, y=value, fill=variable)) +
  geom_boxplot() + guides(fill=FALSE)

```

Trying to create all boxplots in 1 code chunk. This code chunk does not work. I'm still playing around with it.

```{r}
# Remove existing data frame
rm(data)

# Grab comparison columns.
data <- select(beliefs, c(subj, contains("Warmth")))
data <- select(data, -contains("Imp"))

# Remove existing data frame
rm(melt_data)

# Make a tidy data set
melt_data <- melt(data, id="subj")

# Remove existing data frame
rm(data)

# Compare means across brands for each attribute.
ggplot(melt_data, aes(x=variable, y=value, fill=variable)) +
  geom_boxplot() + guides(fill=FALSE)

```

Step 3: Get overall brand attitude predictions

```{r}

# We need to get four Overall Attitudes, one for each brand.
beliefs <- beliefs %>%
  mutate(
    Att_A = Price_Imp*Brand_A_Price + Style_Imp*Brand_A_Style + Durability_Imp*Brand_A_Durability + Comfort_Imp*Brand_A_Comfort + Features_Imp*Brand_A_Features + Warmth_Imp*Brand_A_Warmth,
    Att_B = Price_Imp*Brand_B_Price + Style_Imp*Brand_B_Style + Durability_Imp*Brand_B_Durability + Comfort_Imp*Brand_B_Comfort + Features_Imp*Brand_B_Features + Warmth_Imp*Brand_B_Warmth,
    Att_C = Price_Imp*Brand_C_Price + Style_Imp*Brand_C_Style + Durability_Imp*Brand_C_Durability + Comfort_Imp*Brand_C_Comfort + Features_Imp*Brand_C_Features + Warmth_Imp*Brand_C_Warmth,
    Att_D = Price_Imp*Brand_D_Price + Style_Imp*Brand_D_Style + Durability_Imp*Brand_D_Durability + Comfort_Imp*Brand_D_Comfort + Features_Imp*Brand_D_Features + Warmth_Imp*Brand_D_Warmth
)
# Check them out.
st(select(beliefs, contains("Att")))
```

Brand D has the highest average attitude. We need to test for the First Choice Rule to see if Brand D is the highest choice answer.

Step 4: Get first choice share predictions

```{r}
beliefs <-
  beliefs %>%
    mutate(# Calculate max attitude
           max_att = pmax(Att_A, Att_B, Att_C, Att_D),
           fc_A = Att_A == max_att,
           fc_B = Att_B == max_att,
           fc_C = Att_C == max_att,
           fc_D = Att_D == max_att,
           # Count the number of ties for first.
           nmax = fc_A + fc_B + fc_C + fc_D,
           # and divide by nmax for get the choice share for each winner.
           fc_A = fc_A / nmax,
           fc_B = fc_B / nmax,
           fc_C = fc_C / nmax,
           fc_D = fc_D / nmax
           )
# Check them out.
st(select(beliefs, contains("fc")))
```

Brand A is doing the worst. You can change the importance of the attribute or how people feel about that brand's attribute.

Step 5: Simulate a specific strategy

```{r}
# Change Brand_A_Price to max rating of 10. That only affects Att_A. But that won't be the case for importance changes.
beliefs <- beliefs %>%
  mutate(
    Att_A_new = Price_Imp*10 + Style_Imp*Brand_A_Style + Durability_Imp*Brand_A_Durability + Comfort_Imp*Brand_A_Comfort + Features_Imp*Brand_A_Features + Warmth_Imp*Brand_A_Warmth
) 
beliefs <-
  beliefs %>%
    mutate(# Calculate max attitude
           max_att = pmax(Att_A_new, Att_B, Att_C, Att_D),
           fc_A_new = Att_A_new == max_att,
           fc_B_new = Att_B == max_att,
           fc_C_new = Att_C == max_att,
           fc_D_new = Att_D == max_att,
           # Count the number of ties for first.
           nmax = fc_A + fc_B + fc_C + fc_D,
           # and divide by nmax for get the choice share for each winner.
           fc_A_new = fc_A_new / nmax,
           fc_B_new = fc_B_new / nmax,
           fc_C_new = fc_C_new / nmax,
           fc_D_new = fc_D_new / nmax
           )
# Check them out.
st(select(beliefs, contains("_new")))
```

By chaning the importance of the attribute, the attitudes towards all 4 brands are more evenly distributed.